Figures to insert in text

### 2018-02-25 Chapters/sdm2.tex

Figure \ref{fig:crit-dist-10k-writes} compares the critical distance behavior under different scenarios.  This replicates our previous results and is a first part of the process of framework validation, to which we throw our attention next.

>>>>

Figure \ref{fig:crit-dist-10k-writes} compares the critical distance behavior under different scenarios.  This replicates our previous results \citet{Brogliato2011} and \citet{brogliato2014sparse} and is a first part of the process of framework validation, to which we throw our attention next.
